Footpath Planning for Example-driven Procedural Road Networks

### 2020-03-18 paper/paper.tex
Motivation behind area overlap, explanation for Douglas-Peucker algorithm

(Fan et al., 2014) further discussed how the relative overlap in building area can be used to determine building correspondence between datasets. The relative building overlap between the OSM and SLU datasets will be defined as folows, given the footprints of any building in the OSM set ($foot_{OSM}$) and the SLU set ($foot_{SLU}$):

@@

//TODO: Finding identical points

@@

>>>>

(Fan et al., 2014) further discussed how the relative overlap in building area can be used to determine building correspondence between datasets, in cases where there is not much displacement between OSM building footprints data and the reference data set. Figure X (TODO) shows a typical comparison between the OpenStreetMap and SLU datasets, and by eyesight it was determined that the displacement of features is small. The relative building overlap between the OSM and SLU datasets will be defined as folows, given the footprints of any building in the OSM set ($foot_{OSM}$) and the SLU set ($foot_{SLU}$):

@@

The final problem is that even when building polygons have been matched between the two datasets, they may not have one-to-one vertex relationship. Footprints from different datasets may be formed at a different level of detail. Problems that arise are e.g. that the vertex counts are dissimilar, or that vertex clusters may be found at different parts of the polygon in the two datasets. To avoid this effect, key points are extracted using the Douglas-Peucker algorithm (Douglas and Peucker, 1973), to create a simplifed footprint with less points that still retain information about the rough features of the detailed footprint. The idea behind Douglas-Peucker is to recursively divide a polyline. It initially marks only the start and end points $(v_0, v_n)$ to be kept, and finds the point $v_i$ in between whose distance is the greatest to the line segment between $v_0$ and $v_n$. It then recursively refines the line segments $(v_0, v_i)$ and $(v_i, v_n)$, and proceeds to do so until a line segment $(v_j, v_k)$ is found, where every point in between $v_j$ and $v_k$ have a distance to the line segment $(v_j, v_k)$ that is smaller than some resolution $\epsilon$. Then $v_j$ are added to the simplified polyline, and all nodes in between them are discarded. See Algorithm 1 for a detailed view. In either case The minimum bounding rectangle (MBR) is calculated for the two polygons. Finally the MBR for the OSM building footprint is shifted so that its centroid aligns with the centroid of the MBR of the SLU building footprint. Any edges in the simplified footprints that coinside with the MBR from the same dataset are extracted, and the corresponding points in the original footprints will be matched with each other.

//TODO: Algorithm of Douglas-Peucker

@@

\bibitem{douglas-peucker-73}
Douglas, D.H. and Peucker T.K. 1973. Algorithms for the reduction of the number of points required to \\
represent a digitalized line or its caricature. In: Cartographica: The International Journal for Geographic \\
Information and Geovisualization, 10(2), 112-122. \\
